\begin{center}
  \section*{\abstractname}
\end{center}
\large

With the rapid advancements in technologies over the past few decades, facial recognition has become
ubiquitous in modern days. Despite being a relatively new technology, facial recognition has been
extensively employed in many products we use day-to-day. Large corporations, such as Google, Apple, Microsoft, 
have implemented biometric authentication in their products, enabling their users to incorporate
such features into their daily lives. Intelligence agencies as well as police agencies have been using
such technology to track down criminals and certain targets. Some governments have been using it to automate
border control and even on some trivial tasks such as identifying the text on car plates, reducing a huge amount
of tedious works that would have otherwise been carried out by human manually. Educational organizations
could also benefit from facial recognition by utilizing it to automate roll calls, allowing professors and teachers
to have more time to focus on teaching and allowing students to have more time to spend on learning during classes.
Traditionally, a teacher needs to call each student's name one by one in order to check who is present at a class,
and an entire semester could totally take 90 minutes if every semester consists of 18 weeks and each roll call takes
5 minutes to perform. In this thesis, we combined facial recognition as well as deep metric learning and proposed
a functional roll call automation system which can be practically employed in educational organizations, 
aiding professors to record student attendance. We will also evaluate the practicality of our method by comparing
similar approaches with our methods such as signing into classes by scanning students' ID cards, and
signing in to classes via mobile devices using GPS location tracking. The result of this research is expected to
reduce the chance of fraudulent class sign-ins that could arise in other similar methods, while ensuring the roll calls
could be smoothly automated by our system.
\newpage
