\begin{thebibliography}{10}
  \addcontentsline{toc}{chapter}{Bibliography}

  \bibitem{wem-2018}
  William E. Miller (2018).
  Utilizing Facial Recognition Software to Record Classroom Attendance.

  \bibitem{chc-2012}
  Ching Hisang Chang (2012).
  Smart Classroom Roll Caller System with IOT Architecture.

  \bibitem{zuvio-irs}
  Zuvio IRS,
  An Interactive Educational Tool for Universities.
  \\\texttt{https://www.zuvio.com.tw/student}

  \bibitem{opencv}
  OpenCV (Open Source Computer Vision Library),
  A cross-platform Computer Vision and Machine Learning Library.
  \\\texttt{https://opencv.org/}

  \bibitem{dlib}
  Davis King.
  Dlib,
  A C++ Toolkit Containing Machine Learning Algorithms and Tools to Solve Complex Real World Problems.
  \\\texttt{http://dlib.net/}

  \bibitem{face-recognition}
  Adam Geitgey.\
  face\_recognition,
  The World's Simplest Facial Recognition API for Python and the Command Line.
  \\\texttt{https://github.com/ageitgey/face\_recognition}

  \bibitem{pygtk}
  PyGTK,
  A Convenient Wrapper for GTK+ Library for Use in Python Programs.
  \\\texttt{https://wiki.gnome.org/Projects/PyGTK}

  \bibitem{adrian}
  Adrian Rosebrock (2018).
  Face Recognition with OpenCV, Python, and Deep Learning.
  \\\texttt{https://www.pyimagesearch.com/2018/06/18/face-recognition\-with-opencv-python-and-deep-learning/}

  \bibitem{bib1}
  Himanshu Mallik (2015).
  An Automated Student Attendance Registering System using Face Recognition.

  \bibitem{bib2}
  Abidi, M.A. and Gonzalez, R. C. (1992).
  Data Fusion in Robotics and Machine Intelligence.
  Academic Press, New York.

  \bibitem{bib3}
  Abramson, N. (1963).
  Information Theory and Coding.
  McGraw-Hill, New York.

  \bibitem{bib4}
  Md. Shafiqul Islam, Asif Mahmud, Azmina Akter Papeya, Irin Sultana Onny (2017).
  Real Time Classroom Attendance Management System.

  \bibitem{err-facial-recog-tech}
  AFP (2019)
  Bangkok Post
  \\\texttt{https://www.bangkokpost.com/tech/1820554/study-finds-massive-errors-in-facial-recognition-tech}

\end{thebibliography}
