\chapter{Introduction}
Facial recognition technology has been extensively employed in modern software and products. Nowadays, various factions
such as intelligence agencies, governments and corporations have already been using it to carry out certain tasks.
For instance, Google has implemented biometric authentication in Google Pay, a digital online payment system
which allows its users to make payments using their mobile devices. Apple has introduced \emph{Face ID} to iOS, allowing its users
to unlock their devices with facial recognition technology. Microsoft has developed \emph{Windows Hello} in Windows 10, enabling
Windows 10 users to login via their faces. Other factions such as intelligence and police agencies have been using facial recognition
to identify person of interest.

This technology can also be applied in educational organizations. Since lectures are limited in time, we can try to come up
with a solution to automate roll calls, giving both teachers and students more time to spend on teaching and learning.
If each traditional roll call takes approximately 5 minutes and every semester consists of 18 weeks, then a total of 90 minutes
will be wasted as the semester ends. Therefore, not all professors would perform a roll call every time since it can be time consuming,
and some students would take advantage of it by skipping classes while staying uncaught, leaving the grading results unjustified.

Machine Learning and Facial Recognition technologies have come a long way and they are widely applied in various fields nowadays.
In this thesis, we propose the architecture of a roll call automation system which utilizes \emph{Deep Metric Learning} as well as
\emph{Facial Recognition} to automate the traditional roll call procedures, and we evaluate the practicality of this system 
by comparing alternative approaches with it.

\input{chapters/introduction/facial-recognition}
\input{chapters/introduction/deep-metric-learning}
\input{chapters/introduction/challenges-of-automated-roll-calls}
\input{chapters/introduction/thesis-breakdown}
